Reionization Planck 2018 Notes

### 2020-07-02 results/notes.tex
Updates from Overleaf

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/direct_mcmc_vs_python_kde_and_cosmomc_kde_tanh_tau.png}
\caption{LATEST (to be debugged) -- Added cosmomc KDE version of tau posterior computed with f = 0.14, against python versions with f = 0.1, 0.12, 0.14. They do not agree ... (Note: need to make sure python version had the same covariance matrix, and length of chain ...)
}
\label{fig:}s
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/direct_mcmc_vs_python_kde_and_cosmomc_kde_tanh_tau.png}
\caption{LATEST (to be debugged) -- Added cosmomc KDE version of tau posterior computed with f = 0.14, against python versions with f = 0.1, 0.12, 0.14. They do not agree ... (Note: need to make sure python version had the same covariance matrix, and length of chain ...)
}
\label{fig:}s
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/direct_mcmc_vs_python_kde_and_cosmomc_kde_tanh_tau.png}
\caption{LATEST (to be debugged) -- Added cosmomc KDE version of tau posterior computed with f = 0.14, against python versions with f = 0.1, 0.12, 0.14. They do not agree ... (Note: need to make sure python version had the same covariance matrix, and length of chain ... should probably rerun python version actually.)
}
\label{fig:}s
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/pl18_tanh_highz_test2_run1_vs_relike_tanh_highz_test1_run1_f0p14_tri.png}
\caption{version 1 (has bug that \taulo is not limited to where PCs can model z>6): 2-parameter model 2D plot from cosmomc KDE with f = 0.14 vs direct MCMC.
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/pl18_tanh_highz_test2_run1_vs_relike_tanh_highz_test1_run1_f0p14_taulo_prior_0p0415_tri.png}
\caption{version 2 (added prior \taulo $\leq 0.0415$ for the KDE version, f = 0.14). Direct MCMC chain with the same prior is still running.
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/pl18_tanh_highz_test2_run1_vs_relike_tanh_highz_test1_run1_f0p14_and_f0p20_taulo_prior_0p0415_tri.png}
\caption{version 3, added a curve with f = 0.20 (blue).
}
\label{fig:}
\end{figure}
